\documentclass[conference]{IEEEtran}
%\documentclass[journal,12pt,onecolumn]{IEEEtran}

\ifCLASSOPTIONonecolumn
\usepackage{setspace}
%\doublespacing
\setstretch{1.50}
\fi

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{placeins}
\usepackage{textcomp}
\usepackage{color}
\usepackage{comment}
\usepackage{psfig}
\usepackage{multirow}
\usepackage{steinmetz} % For the phase symbol with the \phase{} command
\usepackage{tabularx}
\setlength{\extrarowheight}{1.5pt}

% Nested comments
\newcommand{\mycomment}[1]{%
}%
\usepackage{environ}
\NewEnviron{nestedcomment}{\mycomment{\BODY}}
% Enables nested comments: \begin{nestedcomment} \begin{comment} \end{comment} \begin{nestedcomment} \end{nestedcomment} \end{nestedcomment}

%\newcommand{\rev}[1]{{\color{blue}#1}}
%\usepackage{xcolor}
%\renewcommand{\theequation}{\Roman{equation}}
%\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%   T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage[font=small,labelfont=bf]{caption}
% Changes the word Table appear not in caps in table captions

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@makecaption}
  {\scshape}
  {}
  {}
  {}
\makeatother
\def\tablename{Table}
\renewcommand{\thetable}{\arabic{table}} %Changes Table numbering from roman to arabic

% Use urltilde in .bib file
\def\urltilde{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}

\begin{document}
\title{Comments on ``A Linear Time Algorithm for the Optimal Discrete IRS Beamforming"
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{The authors are with the Center for Pervasive Communications and Computing (CPCC), Department of Electrical Engineering and Computer Science,
University of California, Irvine.}
\thanks{This work is partially supported by NSF grant 2030029.}
\thanks{This work has been submitted to the IEEE for possible publication. Copyright may be transferred without notice, after which this version may no longer be accessible.}
%\thanks{This work was partially presented at the International Conference on Computing, Networking, and Communications (ICNC) 2023 and the IEEE International Conference on Communications (ICC) 2023.}
}

\ifCLASSOPTIONonecolumn
\author{\IEEEauthorblockN{Dogan Kutay Pekcan, %{\em Student Member, IEEE}}\\
}
\IEEEauthorblockA{\textrm{CPCC, Department of EECS} \\
\textrm{University of California, Irvine, CA, USA}\\
dpekcan@uci.edu\\[7mm]}
\and
\IEEEauthorblockN{ Ender Ayanoglu, {\em Fellow, IEEE}}\\
\IEEEauthorblockA{\textrm{CPCC, Department of EECS} \\
\textrm{University of California, Irvine, CA, USA}
 \\ayanoglu@uci.edu}}
\else
\author{\IEEEauthorblockN{Dogan Kutay Pekcan}
\IEEEauthorblockN{Ender Ayanoglu, {\em Fellow, IEEE}}
}
\fi

\maketitle

\begin{abstract}
Comments on \cite{b1} are provided. Updated necessary and sufficient conditions for its Lemma~1 are given.
Consequently, an updated Algorithm~1 is provided with full specification. Simulation results with improved
performance over the implementation of Algorithm~1 are provided.
\end{abstract}
\begin{IEEEkeywords}
Intelligent reflective surface (IRS), reconfigurable intelligent surface (RIS), discrete beamforming for IRS/RIS.
\end{IEEEkeywords}

\input{introduction}
\input{statements}
\input{algorithm}
\input{results}

%\clearpage\newpage

\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}




