\section{Background}

A $(\dv, \dc)$ LDPC code is a linear block code given by its parity check matrix $\boldsymbol{H}$, which has $\dv$ 1s in each column and $\dc$ 1s in each row. 
SC-LDPC codes divide the codeword into sub-blocks and the parity check equations (check nodes) 
connect neighboring sub-blocks. In this work, we focus on unit-memory SC-LDPC codes~\cite{schmalen2016design}, where only the directly neighboring sub-blocks contribute to the current sub-block. SC-LDPC codes enable a simple windowed decoding scheme~\cite{schmalen2015spatially}.

The authors in~\cite{9594186,9174265} introduced an additional constraint during the construction of SC-LDPC codes, where a fraction of $t$ check nodes (called \emph{coupled checks}, CC) in a sub-block are allowed to connect to other sub-blocks, and the remaining check nodes (\emph{local checks}, LC)  only connect to code bits in the same sub-block. LCs allow us to decode a single sub-block without information from other sub-blocks; the CCs are the bridge to exchange information between sub-blocks. The parity-check matrix of SC-LDPCL codes is composed of $\Blocal$, which defines the LCs and both $\Bleft$ and $\Bright$, which define the CCs and connections to neighboring sub-blocks. This new SC-LDPCL codes offer three decoding modes: separate local decoding, joint decoding of all sub-blocks, and semi-joint decoding. More details of the decoders can be found in \cite{9594186,9174265}. In the remainder of this paper, we use the $(\dv=4, \dc=20, t=\frac14)$ SC-LDPCL code as an example, due to the good decoding performance of these parameters~\cite{schmalen2015spatially,schmalen2016design}.

We employ the concept of SC-LDPCL codes to jointly encode the spatial channels of SDM. SC-LDPCL codes enable a future-proof system design that allows different, scalable and flexible decoders, depending on the application. We assign each sub-block of the SC-LDPCL code to an SDM channel. In the decoder, we either consider decoding of each sub-block separately  (Fig.~\ref{fig_decoding_modes}(a)) or allow an information exchange between the sub-channels (Fig.~\ref{fig_decoding_modes}(b)), which should be kept as little as possible (Fig.~\ref{fig_decoding_modes}(c)). Our work extends SC-LDPCL codes towards communications. In SDM receivers, we aim at limiting information exchange between decoders, possibly requiring slow communication channels on circuit boards between different decoder circuits. We propose two variants of the semi-joint decoder to cope with different levels of information exchange.